# 2022-05-10
# TidyTuesday week 19, NYTimes best sellers
# Data from Post45 Data
---

```{r}
library(readr)
nyt_full <- read_delim("2022-W19/nyt_full.tsv.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)

nyt_titles <- read_delim("2022-W19/nyt_titles.tsv.txt", 
    delim = "\t", escape_double = FALSE, 
    trim_ws = TRUE)
```
Download libraries
```{r}
library(skimr)
library(tidyverse)
library(sentimentr)
library(plotly)
```

Let's get acquainted with the data!
```{r}
skim(nyt_full)
head(nyt_full)

skim(nyt_titles)
head(nyt_titles)
```
### Merge the data and wrangle it 

```{r}
df1 = nyt_titles %>% mutate(title = str_to_title(title))
```

```{r}
df2 = nyt_full %>% filter(title_id %in% df1$id) %>%
  mutate(rank=-1*rank) %>%
  group_by(id=title_id) %>%
  arrange(week) %>%
  summarise(timeline=list(rank),.groups="drop")

df3 = df1 %>% left_join(df2, by="id")
```


```{r}
sentiment=sentiment_by(df3$title)$
head(sentiment)
```


```{r}
df_sentiment <- cbind(df3, sentiment)
df_sentiment

```

```{r}
df_grouped <- df_sentiment %>% filter(ave_sentiment != 0) %>% select(year, ave_sentiment, total_weeks) %>% group_by(year) %>% summarise(mean = mean(ave_sentiment), max = max(ave_sentiment), min = min(ave_sentiment), n_weeks = sum(total_weeks))

head(df_grouped)
  
```
Let's investigate the mean at a simple line chart
```{r}
easy_graph <- ggplot(df_grouped, aes(year, mean)) + 
  geom_line() + theme_minimal()

easy_graph
```

Vizualize min/max as a shadowed territory
```{r}
ggplot(df_grouped, aes(year, mean)) + 
  geom_line() +
  geom_ribbon(aes(year,ymax=max,ymin=min),alpha=0.1) + 
  theme_minimal()
```


```{r}
df_grouped[,c(1,5) ]

df_0 <- 

df_n_weeks <- merge(df_sentiment, df_grouped[,c(1,5) ], year = year)

df_n_weeks <- df_n_weeks %>% filter(ave_sentiment != 0) %>% mutate(year_part = total_weeks/n_weeks, ave_impact = ave_sentiment * year_part)

head(df_n_weeks)

```


```{r}
df_n_weeks %>% slice_min(ave_impact, n = 30)

df_n_weeks %>% slice_min(ave_sentiment, n = 30)
```

```{r}
df_n_weeks
```

Calculate weighted average sentiment, then min/max values.
```{r}
df_grouped_w <-df_n_weeks %>%  select(year, ave_impact, ave_sentiment) %>% group_by(year) %>% summarise(mean = sum(ave_impact), max = max(ave_sentiment), min = min(ave_sentiment))

head(df_grouped_w)
```
Add a date column
```{r}
df_grouped_w$year_date <- as.Date(ISOdate(df_grouped_w$year, 12, 31))

head(df_grouped_w)
```

Bones of the plot
```{r fig.height=6, fig.width=8}
weighted_graph <- ggplot(df_grouped_w, aes(year, mean)) + 
  geom_line(color = "orange", size = 1.2, linetype=3) +
  geom_ribbon(aes(year,ymax=max,ymin=min),alpha=0.1) +
  
  theme_minimal(base_size = 10) + 
  theme(axis.text = element_text(face = "bold"),
        plot.caption = element_text(face = "italic", color = "gray25"),
        plot.title = element_text(size = rel(1.5), face = "bold", color = "navyblue"),
        plot.subtitle = element_text(size = 14, face = "italic", color = "royalblue"),
        axis.title.y = element_text(size = 14, face = "bold", color = "navyblue"), 
        axis.title.x = element_text(size = 12, face = "bold", color = "navyblue"))

weighted_graph
```

Make it interactive with one line of code!
```{r}
weighted_graph <- ggplot(df_grouped_w, aes(year_date, mean)) + 
  geom_line(color = "orange", size = 1.1, linetype=1) +
  geom_ribbon(aes(year_date,ymax=max,ymin=min),alpha=0.1) +
  theme_minimal() + 
  scale_x_date(date_minor_breaks = "10 years") +
  labs(x = "Year", y = "Sentiment",
       title = "Trendy books reflect the year's sentiment!",
       subtitle = "Average, max and min sentiment for NY top books",
       caption = my_caption) +
  theme(axis.text = element_text(face = "bold"),
        plot.caption = element_text(face = "italic", color = "gray25"),
        plot.title = element_text(size = rel(1.5), face = "bold", color = "orange"),
        plot.subtitle = element_text(size = rel(1), face = "bold", color = "royalblue"),
        axis.title.y = element_text(size = rel(1), face = "bold", color = "black"), 
        axis.title.x = element_text(size = rel(1), face = "bold", color = "black"))
        
        
ggplotly(weighted_graph)
          
```

Make annotations studying the data
```{r fig.height=8, fig.width=10}
my_caption <- "#TidyTuesday week 19 | NY Times bestsellers | @TimurZolkin"



weighted_graph <- ggplot(df_grouped_w, aes(year_date, mean)) + 
  geom_line(color = "orange", size = 1.1, linetype=1) +
  geom_ribbon(aes(year_date,ymax=max,ymin=min),alpha=0.1) +
  theme_minimal() + 
  scale_x_date(date_minor_breaks = "10 years") +
  labs(x = "Year", y = "Sentiment",
       title = "Gloomy book titles commanded NY Times in 2020!",
       subtitle = "Weighted average sentiment toppled",
       caption = my_caption) +
  theme(axis.text = element_text(face = "bold"),
        plot.caption = element_text(face = "italic", color = "gray25"),
        plot.title = element_text(size = rel(1.8), face = "bold", color = "darkcyan"),
        plot.subtitle = element_text(size = rel(1.3), face = "bold", color = "black"),
        axis.title.y = element_text(size = rel(1), face = "bold", color = "black"), 
        axis.title.x = element_text(size = rel(1), face = "bold", color = "black")) +
  
  annotate(geom = "curve", x = as.Date("1933-12-31"), y = -0.707, xend = as.Date("1939-12-31"), yend = -1, curvature = .3, linetype = 2) +
  annotate(geom = "text", x = as.Date("1940-12-31"), y = -1, label = "Anthony Adverse, 1933", hjust = "left", color = "Red2", size = 4, fontface = 2) +
  
  annotate(geom = "curve", x = as.Date("1959-12-31"), y = -1.1547005, xend = as.Date("1966-12-31"), yend = -1.25, curvature = .3, linetype = 2) +
  annotate(geom = "text", x = as.Date("1966-12-31"), y = -1.25, label = "Too Many Ghosts, 1959", hjust = "left", color = "Red2", size = 4, fontface = 2) +
  
    annotate(geom = "curve", x = as.Date("2019-12-31"), y = -1.4142136	, xend = as.Date("2011-12-31"), yend = -0.9, curvature = .3, linetype = 2) +
  annotate(geom = "text", x = as.Date("2011-12-31"), y = -0.9, label = "Liar Liar, 2019", hjust = "right", color = "Red2", size = 4, fontface = 2) +

annotate(geom = "curve", x = as.Date("2006-12-31"), y = -1.4142136	, xend = as.Date("1999-12-31"), yend = -1.1, curvature = .5, linetype = 2) +
  annotate(geom = "text", x = as.Date("1999-12-31"), y = -1.1, label = "Definitely Dead, 2006", hjust = "right", color = "Red2", size = 4, fontface = 2) +
  
  annotate(geom = "curve", x = as.Date("1971-12-31"), y = -1	, xend = as.Date("1980-12-31"), yend = -0.7, curvature = .3, linetype = 2) +
  annotate(geom = "text", x = as.Date("1980-12-31"), y = -0.7, label = "Nemesis, 1971", hjust = "left", color = "Red2", size = 4, fontface = 2) +
  
  annotate(geom = "curve", x = as.Date("1991-12-31"), y = 1.4310835	, xend = as.Date("1980-12-31"), yend = 1.3, curvature = .3, linetype = 2) +
  annotate(geom = "text", x = as.Date("1980-12-31"), y = 1.3, label = "Loves Music, Loves To Dance, 1991", hjust = "right", color = "Green4", size = 4, fontface = 2) +
  annotate(geom = "curve", x = as.Date("1932-12-31"), y = 1.1313708	, xend = as.Date("1935-12-31"), yend = 1, curvature = .3, linetype = 2) +
  annotate(geom = "text", x = as.Date("1935-12-31"), y = 1, label = "Benefits Received, 1932", hjust = "left", color = "Green4", size = 4, fontface = 2) +
  
  annotate(geom = "curve", x = as.Date("2008-12-31"), y = 1.4142136	, xend = as.Date("2003-12-31"), yend = 1, curvature = .3, linetype = 2) +
  annotate(geom = "text", x = as.Date("2003-12-31"), y = 1, label = "Divine Justice, 2008", hjust = "Right", color = "Green4", size = 4, fontface = 2) +
  
  annotate(geom = "curve", x = as.Date("2016-12-31"), y = 1.10227046	, xend = as.Date("2009-12-31"), yend = 0.6, curvature = .3, linetype = 2) +
  annotate(geom = "text", x = as.Date("2009-12-31"), y = 0.6, label = "Tom Clancy: True Faith And Allegiance, 2016", hjust = "right", color = "Green4", size = 4, fontface = 2) +
  
  annotate(geom = "text", x = as.Date("2012-12-31"), y = -0.4, label = "Range of title sentiment", hjust = "right", color = "Gray45", size = 5, fontface = 2) +
  
  annotate(geom = "curve", x = as.Date("1934-12-31"), y = 0	, xend = as.Date("1940-12-31"), yend = 0.3, curvature = .3, linetype = 2) +
  annotate(geom = "text", x = as.Date("1940-12-31"), y = 0.35, label = "Weighted Average Sentiment", hjust = "left", color = "Orange1", size = 5, fontface = 2)
  
 

weighted_graph
```

```{r}
#df_n_weeks %>% slice_min(ave_impact, n = 30)

df_n_weeks %>% slice_max(ave_sentiment, n = 50) %>% select(year, title, ave_sentiment)
```


-----------------

```{r}
install.packages("ggpubr")
library(ggpubr)
```

```{r}
ggarrange(weighted_graph, easy_graph, ncol = 1, nrow = 2, heights = c(1, 0.7))
```

```{r}

``````{r}

```

```{r}

```
