---
title: "TidyTuesday Home prices"
output: html_document
date: '2022-07-05'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1. Download packages and data
```{r}
#install.packages("readr")
#install.packages("lubridate")
#install.packages("scales")
#install.packages("tidyverse")
#install.packages("skimr")
#install.packages("corrplot")
#install.packages("gridExtra")
#install.packages("caret")
#install.packages("GGally")


library(corrplot)
library(caret)
library(gridExtra)
library(skimr)
library(tidyverse)
library(lubridate)
library(GGally)
library(scales)
```

```{r}
rent <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-07-05/rent.csv')
permits <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-07-05/sf_permits.csv')
new_construction <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-07-05/new_construction.csv')
```

## Exploratory Data Analysis
### 2.1 Data Size and structure

```{r}
skim(permits)
head(permits)
```


```{r}
skim(rent)
head(rent)
```
### 2.2 Exploring rent data
```{r}
my_pretty_theme <- theme_minimal(base_family = "Roboto Condensed", base_size = 12) +
  theme(panel.grid.minor = element_blank(),
        # Bold, bigger title
        plot.title = element_text(face = "bold", size = rel(1.7)),
        # Plain, slightly bigger subtitle that is grey
        plot.subtitle = element_text(face = "plain", size = rel(1.3), color = "grey70"),
        # Italic, smaller, grey caption that is left-aligned
        plot.caption = element_text(face = "italic", size = rel(0.7), 
                                    color = "gray50"),
        # Bold legend titles
        legend.title = element_text(face = "bold"),
        # Bold, slightly larger facet titles that are left-aligned for the sake of repetition
        strip.text = element_text(face = "bold", size = rel(1.1), hjust = 0),
        # Bold axis titles
        axis.title = element_text(face = "bold"),
        # Add some space above the x-axis title and make it left-aligned
        # axis.title.x = element_text(margin = margin(t = 10), hjust = 0),
        # Add some space to the right of the y-axis title and make it top-aligned
        axis.title.y = element_text(margin = margin(r = 10), hjust = 1),
        # Add a light grey background to the facet titles, with no borders
        strip.background = element_rect(fill = "grey90", color = NA),
        # Add a thin grey border around all the plots to tie in the facet titles
        panel.border = element_rect(color = "grey90", fill = NA))
```


```{r}
caption <- "TidyTuesday 2022 W27 | K. Pennington Rental Housing Data | @TimirZolkin"

rent_p <- rent[!is.na(rent$price), ] %>%
  ggplot(aes(x = price)) +
  geom_histogram(fill = "navyblue", binwidth = 300, alpha = 0.8) +
  scale_x_continuous(breaks = seq(0, 40000, by = 10000), labels = comma)+
  geom_text(x = 35000, y = 10000, label = "Max value here", color = "tomato1")+
  labs(title = "Rent price distribution, San Francisco",
       caption = caption) +
  my_pretty_theme +
    theme(axis.title.y = element_blank())

rent_p  
#   geom_curve(aes(x = 35000, y = 9000, xend = 40000, yend = 0),
#             arrow = arrow(length = unit(0.03, "npc")))+
max(rent$price)
```


```{r}
rent_exp_p <- rent[!is.na(rent$price), ] %>%
  ggplot(aes(x = price)) +
  geom_histogram(fill = "navyblue", binwidth = 300, alpha = 0.8) +
  scale_x_continuous(breaks = seq(0, 40000, by = 10000), labels = comma)+
  coord_cartesian(ylim = c(0, 300), xlim = c(10000, 40000))+
  labs(title = "High Rent price distribution, San Francisco",
       caption = caption, colour = "grey79") +
    my_pretty_theme +
    theme(axis.title.y = element_blank())

rent_very_exp_p <-  rent[!is.na(rent$price), ] %>%
  ggplot(aes(x = price)) +
  geom_histogram(fill = "navyblue", binwidth = 300, alpha = 0.8) +
  scale_x_continuous(breaks = seq(0, 40000, by = 10000), labels = comma)+
  coord_cartesian(ylim = c(0, 20), xlim = c(20000, 40000))+
  #fill labs with "" to hold title and caption squares empty
  labs(title = "", caption = "") +
    my_pretty_theme +
    theme(axis.title.y = element_blank())

rent_exp_p
```

```{r}
# install.packages("ggpubr")
library(ggpubr)
```

```{r fig.height=6, fig.width=10}
ggarrange(rent_exp_p, rent_very_exp_p,
        ncol = 2, nrow = 1)
```


### 1.3 Correlation plots

```{r}
ggcorr(rent %>% select(where(is.numeric), -date, - year), palette = "RdBu", label = TRUE)
```


```{r}
#index vector numeric variables
numericVars <- which(sapply(rent, is.numeric))

numericVarNames <- names(numericVars)
cat('There are', length(numericVars), 'numeric variables')
```
source:https://www.kaggle.com/code/erikbruin/house-prices-lasso-xgboost-and-a-detailed-eda
```{r}
rent_numVar <- rent[, numericVars] %>% select(-date)
cor_numVar <- cor(rent_numVar, use="pairwise.complete.obs") #correlations of all numeric variables

#sort on decreasing correlations with SalePrice
cor_sorted <- as.matrix(sort(cor_numVar[,'price'], decreasing = TRUE))
 #select only high corelations
CorHigh <- names(which(apply(cor_sorted, 1, function(x) abs(x)>0.2)))
cor_numVar <- cor_numVar[CorHigh, CorHigh]

CorHigh

corrplot.mixed(cor_numVar, tl.col="black", tl.pos = "lt")
```

We see that rent.csv file gives us an overview of rent ads in SF for years 2003-2017. 

Rent prices are somewhat related to number of beds, baths and apartment area as plots below are indicating.

Obviously there is some information value in investigating appartment locaton and other variables.


Room in apt variable in not very informative
```{r}
rent %>% select(room_in_apt) %>% count(room_in_apt)
```

```{r}
summary(rent)
```


#### 2.2.1 Basic Linear regression diagnostics for rent data
```{r}
summary(lm(price ~ beds + baths +sqft, data = rent %>% filter(year == 2015)))
```

```{r}
install.packages("car")
library(car)
```

```{r}
fit_rent_test <- lm(price ~ beds + baths +sqft, data = rent %>% filter(year == 2015))
```

```{r fig.height=6, fig.width=6}
residualPlot(fit_rent_test)
qqPlot(fit_rent_test)
```

```{r}
plot(lm(price ~ beds + baths +sqft, data = rent %>% filter(year == 2015)))
```
#### 2.2.2 Exploring price of a room 

```{r}
rent <- rent %>% mutate(date = ymd(date))
```

```{r}
rent <- rent %>% mutate(month_end = ceiling_date(date, "month") - days(1))
head(rent)
```


```{r}
#rent <- rent %>% mutate(y_quarter = quarter(date, with_year = T))
rent <- rent %>% mutate(county = str_to_title(county))

skim(rent)
```

```{r}
rent %>% filter(year == 2007)
```


Let's try to visualize rent price per sqft or room in different counties

```{r}
#install.packages("MetBrewer")
#library(MetBrewer)
MetBrewerpalette <- met.brewer("Hiroshige", n = 10, type = "discrete")
```



```{r}
my_pretty_theme_2 <- theme_minimal(base_family = "Roboto Condensed", base_size = 12) +
  theme(panel.grid.minor = element_blank(),
        # Bold, bigger title
        plot.title = element_text(face = "bold", size = rel(1.7)),
        # Plain, slightly bigger subtitle that is grey
        plot.subtitle = element_text(face = "plain", size = rel(1.3), color = "grey70"),
        # Italic, smaller, grey caption that is left-aligned
        plot.caption = element_text(face = "italic", size = rel(0.7), 
                                    color = "grey70", hjust = 0),
        # Bold legend titles
        legend.title = element_text(face = "bold"),
        # Bold, slightly larger facet titles that are left-aligned for the sake of repetition
        strip.text = element_text(face = "bold", size = rel(1.1), hjust = 0),
        # Bold axis titles
        axis.title = element_text(face = "bold"),
        # Add some space above the x-axis title and make it left-aligned
        # axis.title.x = element_text(margin = margin(t = 10), hjust = 0),
        # Add some space to the right of the y-axis title and make it top-aligned
        #axis.title.y = element_text(margin = margin(r = 10), hjust = 1),
        # Add a light grey background to the facet titles, with no borders
        strip.background = element_rect(fill = "grey90", color = NA),
        # Add a thin grey border around all the plots to tie in the facet titles
        panel.border = element_rect(color = "grey90", fill = NA))
```


```{r fig.height=6, fig.width=10}
p <- rent[!is.na(rent$price), ] %>%
  #filter(year == 2018) %>%
  drop_na(county) %>%
  group_by(year, county) %>% summarise(price = mean(price)) %>%
  ggplot(aes(x = year, y = price, fill = county)) +
  geom_col()+
  facet_wrap(~county, ncol = 2) +
  scale_fill_manual(values = MetBrewerpalette) +
  scale_y_continuous(breaks = c(0, 2000, 4000), labels=scales::dollar_format())+
  scale_x_continuous(breaks = c(2000, 2005, 2010, 2015, 2019))+
  my_pretty_theme+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major = element_blank(),
        legend.position="none")+
  labs(title = "Rental Housing in California: An Overview", subtitle = "Average rent prices based on Craiglist data, 2000-2019", caption = "TidyTuesday W-27 2022 | K. Pennington Rental Housing Data | by @TimirZolkin")
    
p  
```



```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```

v
```{r}

```


```{r}

```


```{r}

```


```{r}

```

vv